Verifying Demonstrations

### 2018-11-13 paper/verifiability-analysis.tex
WIP on rewamping verifiability analysis

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify that their participation proofs (\ie proof shares) are indeed included in the count computed.
All proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, \pi_{\wid}\)) are committed to the blockchain and available from a public and permanent storage (see \cref{fig:ProtocolOverview}).
Thus, Alice and Bob can simply check that all of their proof shares are indeed there and the security of individual verifiability depends on the properties of the blockchain and storage.

\Cref{UniversalVerif}  includes that anyone can check the result and that all participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\pi_\pid,
\pi_{\wid}\)) of the proofs and count them.
As for individual verifiability, the security of universal verifiability is reduced to the properties of the blockchain and storage but also the eligibility verification, which we will discuss next.

@@

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \PRIVO, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
We will now analyze these properties.

@@

\Cref{TemporallyRelated} ensures freshness, as Alice cannot simply resubmit an old proof as a new one.
In general, freshness requires the prover to respond to an unpredictable challenge.
The challenge here is to include the hash value at the head of the blockchain at the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof share).
As it is the case in the construction of blockchains, the hash value at the head depends on the previous blocks in the chain.
Thus, the predictability of \(t_s\) depends on the predictability of the blocks, which depends on the predictability of the transactions and the nonce needed by the miner.
In turn, the transactions depend on the signatures made by the signing keys corresponding to the used transactions.
If these were predictable, the adversary could conduct arbitrary transactions in the blockchain --- which is assumed to be hard by design.
Thus, Alice can predict \(t_s\) only with negligible probability, as \(t_s\) must have been published on the blockchain before being included in her proof share.

>>>>

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \pi_\pid, \pi_{\wid})\)) are committed to the ledger and 
available from a public and permanent storage (see 
\cref{fig:ProtocolOverview}).
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger and storage (\(\TS\), \cref{timestamp}).
(As these are the main properties of distributed ledgers, we do not elaborate 
further.)

\Cref{UniversalVerif} includes that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\pi_\pid,
\pi_{\wid}\)) of the proofs and count them.
As for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger and storage; but universal 
verifiability also depends on the eligibility verification, which we will 
discuss next.

@@

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \PRIVO, we have several attributes that must be verifiable: the time of 
creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 
location of \(\sk_P\) at creation (\ie, spatial eligibility, 
\cref{SpatiallyRelated}), recognition of two proofs originating from the same 
person (\ie, one-proof-per-person eligibility, \cref{CountOnce}) and that the 
proof is indeed designated for the event (\ie, designated-event eligibility, 
\cref{DesignatedEvent}).
We will now analyze these properties.

@@

\Cref{TemporallyRelated} ensures freshness, as Alice cannot simply resubmit an 
old proof as a new one or create a proof in advance.

In general, to prevent replays, Alice must respond to an unpredictable 
challenge.
The challenge here is the hash value of the head block of the ledger at the 
time of the proof's creation (\(\TSget\)).
The response is simply the challenge itself and is included as \(t_s\) and 
\(t_s'\) in the proof share (see \cref{fig:ProofFig}).

As it is the case in the construction of blockchains, the hash value at the 
head depends on the previous blocks in the chain.
Thus, the predictability of \(t_s\) depends on the predictability of the blocks, which depends on the predictability of the transactions and the nonce needed by the miner.
In turn, the transactions depend on the signatures made by the signing keys 
corresponding to the used transactions --- which depends on uniformly random 
nonces.
If these were predictable, the adversary could conduct arbitrary transactions in the blockchain --- which is assumed to be hard by design.
Thus, Alice can predict \(t_s\) only with negligible probability, as \(t_s\) must have been published on the blockchain before being included in her proof share.

Also, the correctness of the challenge must be verifiable by any verifier 
(\(\TStime\)).
